---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

All implementation and documentation is an extension of Jennifer Bryan's [foofactors package.](https://github.com/jennybc/foofactors)

**NOTE: This is a toy package created for expository purposes. It is not meant to actually be useful. If you want a package for factor handling, please see [forcats](https://cran.r-project.org/package=forcats).**

### foofactors

Factors are a very useful type of variable in R, but they can also drive you nuts. This package provides some helper functions for the care and feeding of factors.

### Installation

```{r installation, eval = FALSE}
devtools::install_github("jmurthy12/foofactors")
```



### Quick demo

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work. Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

#### 1) Function : freq_out()

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

###### Unit Test
Link for unit test is avalable [here](https://github.com/jmurthy12/foofactors/blob/master/tests/testthat/test_freq_out.R)


#### 2) Function : fbind()

Let's try fbind() on data sets "cars" and "mtcars"
```{r}
str(mtcars)
```

```{r}
str(cars)
```

```{r}
fbind(mtcars$cyl[c(2, 3, 5)], cars$speed[c(1, 2, 3)])
```

Let's work on Iris data set as suggested in class
```{r}
str(iris)
```
###### Unit Test
Link for unit test is avalable [here](https://github.com/jmurthy12/foofactors/blob/master/tests/testthat/test_fbind.R)


I've made changes to Jenny Bryan's document starting from the below section. 



#### 3) Function : check_factor_character()
check_factor_character() determines if factors are required

Returns :

TRUE : If factors are not required
FALSE : If factors are required (i.e.., factors are not characters)

```{r}
check_factor_character(iris$Species)
#> [1] FALSE
```

###### Unit Test
Link for unit test is avalable [here](https://github.com/jmurthy12/foofactors/blob/master/tests/testthat/test_check_factor_character.R)


#### 4) Function : reorder_descending()
reorder_descending() reorders the factor levels in descending order,this is used especially in plots as already discussed in fct_reorder() section of [Homework 5](https://github.com/jmurthy12/STAT545-hw-murthy-janani/blob/master/hw05/hw05.md)

```{r}
levels(iris$Species)
levels(reorder_descending(iris$Species))
```

###### Unit Test
Link for unit test is avalable [here](https://github.com/jmurthy12/foofactors/blob/master/tests/testthat/test_reorder_descending.R)


#### 5) Function : factor_as_orginal()
 factor_as_orginal() re-orders the factor levels same as input data 
```{r}
library(gapminder)
factor_as_orginal(gapminder$continent)
```


###### Unit Test
Link for unit test is avalable [here](https://github.com/jmurthy12/foofactors/blob/master/tests/testthat/test_factor_as_orginal.R)
