---
title: "foofactors"
author: "Janani Murthy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Tite}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

All implementation and documentation of `fbind()` and `freq_out` are based on Jennifer Bryan's [foofactors package.](https://github.com/jennybc/foofactors)

Factors are a very useful type of variable in R, but they can also drive you nuts. Especially the "stealth factor" that you think of as character.

Can we soften some of their sharp edges?

#### 1) Function : fbind()

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work.  Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

#### 2) Function : freq_out()
The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

I've made changes to Jenny Bryan's document starting from the below section. 

Binding data sets "cars" and "mtcars" using fbind()
```{r}
fbind(mtcars$cyl[c(2, 3, 5)], cars$speed[c(1, 2, 3)])
```


#### 3) Function : check_factor_character()
check_factor_character() determines if factors are required

Returns :

TRUE : If factors are not required

FALSE : If factors are required (i.e.., factors are not characters)

```{r}
check_factor_character(iris$Species)
#> [1] FALSE
```

#### 4) Function : reorder_descending()
reorder_descending() reorders the factor levels in descending order,this is used especially in plots as already discussed in fct_reorder() section of [Homework 5](https://github.com/jmurthy12/STAT545-hw-murthy-janani/blob/master/hw05/hw05.md)

```{r}
levels(iris$Species)
levels(reorder_descending(iris$Species))
```

#### 5) Function : factor_as_orginal()
 factor_as_orginal() re-orders the factor levels same as input data 
```{r}
data_1 <- c("Asia","Africa","Americas","Europe","Oceania")
factor_as_orginal(data_1)
